Integrating brain and biomechanical models - a new paradigm for understanding neuro-muscular control

### 2017-11-17 papers/integration/omm_integ.tex
Work in progress on changes responding to R2's comments

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{James {et~al.}}
\def\Authors{Sebastian James\,$^{1,2,*}$, Chris Papapavlou\,$^5$, Alexander Blenkinsop\,$^{1,2}$, \\
  Alexander Cope\,$^3$,  \\
  Sean Anderson\,$^{2,4}$, Konstantinos Moustakas\,$^5$, Kevin Gurney\,$^{1,2}$}

@@

Many neural populations are involved in the coding of saccadic eye
movements, only a very brief overview is given here; for a review,
see \cite{munoz_commentary:_2002}. One pathway takes information from
the retina directly into the superficial layers of the superior
colliculus in the brainstem
\citep{sterling_receptive_1971,linden_massive_1983,wu_involvement_1994}.
Activity within the superior colliculus then excites neurons in the
pons, medulla and rostral mid-brain \citep{sparks_brainstem_2002}.
and \rvw{finally the motor neurons} which innervate the extraocular muscles
\citep{fuchs_firing_1970,sparks_brainstem_2002}. This direct pathway
is responsible for the low latency saccades called express saccades
\citep{schiller_effect_1987,edelman_activity_1996}.
%
Information from the retina is also processed by visual cortex which
feeds through to the frontal eye fields in which activity is related
to reflexive and voluntary
saccades \citep{schall_neural_1999}. Activity build-up in the frontal
eye fields is transferred to the intermediate layers of the superior
colliculus
\citep{stanton_frontal_1988-1} and is also processed by the basal ganglia,
which participates in the selection of the winning saccade end point
\citep{stanton_frontal_1988}.
%
Although both cortical and subcortical paths produce a saccade target
signal in the superior colliculus, it is also possible for animals to
make relatively normal saccades even after the colliculus has been
ablated
\citep{wurtz_activity_1972,aizawa_reversible_1998},
though express saccades are lost with collicular lesions
\citep{schiller_effect_1987}. This makes the superior colliculus
a perplexing structure, being both critically involved in saccade
target specification \citep{sparks_sensory_1987} and saccade dynamic control
\citep{waitzman_superior_1991,goossens_optimal_2012} and yet dispensible.
The `backup pathway' likely incorporates the oculomotor vermis and
fastigial oculomotor region of the cerebellum which are known to
participate in the specification, dynamics and adaptation of saccadic
eye movements \citep{kleine_saccade-related_2003,takagi_effects_1998}.

@@

% A very short introduction to the section.
The integrated brain and biomechanical model described here is a
development of the model in \cite{cope_basal_2017},
referred to here as the \ccg~model. This was a rate-coded neural
network model incorporating retinal populations, frontal eye fields
(FEF), the basal ganglia (BG), and the superior colliculus (SC). In
the \ccg~model, the centroid of the activity in the deep
layers of superior colliculus was assumed to accurately encode the
location of the eye at the end of the saccade
\citep{wurtz_activity_1972,robinson_eye_1972,van_gisbergen_collicular_1987,mcilwain_lateral_1982}.
This location was used to recalculate the positions of the luminances
in the eye's frame of reference at each time step. The model included
no brainstem populations other than superior colliculus, nor a
neuromuscular model.

To summarize, the \ccg~model takes as \e{input} the positions of
luminances on a topographic map and produces as output a saccade
target.

@@

The brain model, excluding the brainstem, is a re-implementation of
the \ccg~model, \rvwt{of reflexive saccadic behaviour}.
%
\rvwt{Reflexive saccades are fast eye movements elicited by abrupt
changes in the peripheral visual scene (reflexive saccades can occur
also as a result of auditory and somatosensory stimuli, but these
modalities are ignored here are in \cite{cope_basal_2017}). A
reflexive saccade has a starting position defined by the initial
orientation of the eye and an end-point position in which the eye is
directed towards a new target. Regardless of the number of targets
within the visual scene, the brain must choose one location as the
end-point, because the eyes can only look in one direction at a
time. The functionality reproduced by the \ccg~model is `the selection
of the best target end-point for a reflexive saccade'. A competition
such as this between competing, incompatible movements is often
referred to as an \e{action selection}
problem \citep{norman_attention_1986,maes_dynamics_1989,redgrave_basal_1999}.}

\rvwt{It is thought that in vertebrates, the basal ganglia (BG) play
an important r\^ole in action selection
\citep{mink_basal_1996,graybiel_basal_1998,hikosaka_role_2000}.
The \ccg~model places the BG at the centre of the oculomotor system,
following the known anatomy of the region.  The BG receives excitatory
inputs directly from retinotopic regions of the cortex including the
frontal eye fields (FEF), supplementary eye fields (SEF), lateral
intraparietal cortex (LIP) and dorsolateral prefrontal cortex. The BG
receives input indirectly from the superior colliculus, which also has
a retinotopic arrangement. The dorsolateral prefrontal cortex, which
participates in voluntary saccades
\citep{funahashi_prefrontal_1993,munoz_look_2004}, is not
modelled because the model concerns reflexive rather than voluntary
eye movements. Several other regions of the brain that are associated
with eye movements are also omitted from the model. The early visual
processing stream in cortex, from V1, through to the LIP is subsumed
into a `sustained retinal' signal. The justification here is that the
model reacts to simple luminant targets and does not need to carry out
the feature extraction performed by these visual areas. The
supplementary eye fields are involved in the programming of
saccades \citep{} and memory guided saccades \citep{}. Lesions of SEF
do not affect visually guided saccades \citep{} and so the SEF is also
omitted from the model.
%
% Figure here is the ``macroscopic architecture'' one.
%
The
BG's output is inhibitory and shapes the build-up of activity in both
of these regions.
%
The \ccg~model adopts a `channel based' model from previous
work~\citep{redgrave_basal_1999,gurney_basal_2004}. Within the context
of the basal ganglia model, a `channel' is a sub-set of neurons which
are associated with an individual action. Each channel in BG loops back via
relays in the thalamus through cortex. Input into this
thalamo-cortical loop is
termed `salience'. Because it is a loop, input salience to the channel
may originate cortically or sub-cortically. The higher the salience of
the channel, the greater is the behavioural relevance of the
associated action.

In the oculomotor model, an action
corresponds to a distinct saccade end point. It can be seen that the
action space for reflexive saccade end points is therefore
continuous rather than descrete.}

Fig.~\ref{brain_model} shows the layout of the populations in the
brain model and the interconnections between them. Each population of
2500 elements is arranged as a 50 by 50 grid which forms a map in a
retinotopic co-ordinate system, roughly matching the known layout of
the superior colliculus \citep{robinson_eye_1972}.
% and frontal eye field?

@@

The output, $y$, of LINlinear is related to the activation $a$ by the
piecewise linear transfer function
\begin{equation}
   y(a) = \begin{cases}
      0   & a < c \\
      a-c & c \leq a \leq 1+c \\
      1   & a > 1+c
   \end{cases}
\end{equation}
where $c$ is a parameter defining the slope of the transfer
function. At this point, the naming scheme for the component becomes
apparent; this is a Leaky Integrator with a piecewise-linear transfer
function.

@@

The D1MSN and D2MSN components are both leaky integrators, similar to
LINlinear. They differ in that they have no shunting inhibition. They
are used to model medium spiny neuron (MSN) populations in the
striatum. As they model the fact that most MSN neurons fall into two
groups; those expressing D1 dopamine receptors and those expressing D2
receptors, they have a dopamine parameter that modulates the input
activation, so that their equations for $a_{in}$ are thus:
\begin{equation}
   a_{in}^{D1} = (0.2 + d)A + 0.01 R_N
\end{equation}
\begin{equation}
   a_{in}^{D2} = (1 - d)A + 0.01 R_N
\end{equation}
where $d$ is the dopamine parameter. Varying dopamine from 0 to 1
enhances the activation in the D1 model, whereas it decreases the
activation of the D2 model elements, in line with experimental
observations \citep{harsing_influence_1997,gonon_prolonged_1997}.
Note that the equation for $a_{in}^{D1}$ differs from that used in
the \ccg~model, for which the cortico-striatal weights are multiplied
by $(1+d)$ rather than $(0.2+d)$.

@@

\cite{tabareau_geometry_2007} gives a formulation for the weight maps
in which it is possible to project both a positive and a negative
weight. In our model, all projections from SC\_deep are excitatory.
This means that each channel has a weight which follows the form:
\begin{equation} \label{eq:weightmaps}
w(r,\phi) = i\;e\,^{jr}\;\sin\left(\frac{2\pi\phi}{W_{nfs}} + k\right)
\end{equation}
where $i$, $j$ and $k$ are per-channel parameters for the weight
maps. $k$ is determined by the mapping. Only the positive part of the
sine is utilised. $i$ and $j$ are parameters to be found.

@@

% worldDataMaker to brain, but Re-work:
The eye model outputs its rotational state at each timestep. The
rotational state is used to compute the view of the world in the eye's
frame of reference. To simplify the calculation, the luminances exist
on a spherical surface at the centre of which is the eye. A hand-coded
BRAHMS component called worldDataMaker computes the projection of the
luminances into the eye's frame of reference and then converts this
representation into a retinotopic map to pass into the brain
model. The input to the brain model is thus able to change
continuously, on every timestep, rather than in a step-wise fashion
when a saccade occurs, as in the \ccg~model.

@@

>>>>

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{James {et~al.}}
\def\Authors{Sebastian James\,$^{1,2}$, Chris Papapavlou\,$^5$, Alexander Blenkinsop\,$^{1,2}$, \\
  Alexander Cope\,$^3$,  \\
  Sean Anderson\,$^{2,4}$, Konstantinos Moustakas\,$^5$, Kevin Gurney\,$^{1,2,*}$}

@@

Many neural populations are involved in the coding of saccadic eye
movements, only a very brief overview is given here; for a review,
see \cite{munoz_commentary:_2002}. One pathway takes information from
the retina directly into the superficial layers of the superior
colliculus in the brainstem
\citep{sterling_receptive_1971,linden_massive_1983,wu_involvement_1994}.
Activity within the superior colliculus then excites neurons in the
pons, medulla and rostral mid-brain \citep{sparks_brainstem_2002}.
and \rvw{finally the motor neurons} which innervate the extraocular muscles
\citep{fuchs_firing_1970,sparks_brainstem_2002}. This direct pathway
is responsible for the low latency saccades called express saccades
\citep{schiller_effect_1987,edelman_activity_1996}.
%
Information from the retina is also processed by visual cortex which
feeds through to the frontal eye fields in which activity is related
to reflexive and voluntary
saccades \citep{schall_neural_1999}. Activity build-up in the frontal
eye fields is transferred to the intermediate layers of the superior
colliculus
\citep{stanton_frontal_1988-1} and is also processed by the basal ganglia,
which participates in the selection of the winning saccade end point
\citep{stanton_frontal_1988,hikosaka_role_2000}.
%
Although both cortical and subcortical paths produce a saccade target
signal in the superior colliculus, it is also possible for animals to
make relatively normal saccades even after the colliculus has been
ablated
\citep{wurtz_activity_1972,aizawa_reversible_1998},
though express saccades are lost with collicular lesions
\citep{schiller_effect_1987}. This makes the superior colliculus
a perplexing structure, being both critically involved in saccade
target specification \citep{sparks_sensory_1987} and saccade dynamic control
\citep{waitzman_superior_1991,goossens_optimal_2012} and yet dispensible.
The `backup pathway' likely incorporates the oculomotor vermis and
fastigial oculomotor region of the cerebellum which are known to
participate in the specification, dynamics and adaptation of saccadic
eye movements \citep{kleine_saccade-related_2003,takagi_effects_1998}.

@@

% A very short introduction to the section.
The integrated brain and biomechanical model described here is a
development of the model in \cite{cope_basal_2017}, referred to here
as the \ccg~model. This was a rate-coded neural network model
incorporating retinal populations, frontal eye fields (FEF), the basal
ganglia (BG), and the superior colliculus (SC).  The \ccg~model takes
as \e{input} the positions of luminances \rvwt{(of fixed shape and
intensity)} on a topographic map. \rvwt{Whilst certain assumptions
were made about the input---that a luminant input excites activity on
a retinotopic layer, with computer code carrying out the
transformation achieved in the brain by a neural connectivity
map \citep{thivierge_topographic_2007}---it is nonetheless \e{not} an
input-assumption model according to our definition because the
activity generated in the neural input layer is modelled as a response
to the luminances, rather than being crafted.}  In the \ccg~model, the
centroid of the activity in the deep layers of superior colliculus was
assumed to accurately encode the location of the eye at the end of the
saccade
\citep{wurtz_activity_1972,robinson_eye_1972,van_gisbergen_collicular_1987,mcilwain_lateral_1982}.  This location was used to
recalculate the positions of the luminances in the eye's frame of
reference at each time step. \rvwt{Because a pattern of neural
activity in the output population was assumed to have a behavioural
outcome, it was thus an \e{output-assumption model}}.  The model
included no brainstem populations other than superior colliculus, nor
a neuromuscular model.

@@

% Describe what is modelled first
The brain model, excluding the brainstem, is a re-implementation of
the \ccg~model, \rvwt{of reflexive saccadic behaviour \citep{cope_basal_2017}}.
\rvwt{Reflexive saccades are fast eye movements elicited by abrupt
changes in the peripheral visual scene (reflexive saccades can occur
also as a result of auditory and somatosensory stimuli, but these
modalities are ignored in this model). A reflexive saccade has a
starting position defined by the initial orientation of the eye and an
end-point position in which the eye is directed towards a new
target. Regardless of the number of targets within the visual scene,
the brain must choose one location as the end-point, because the eyes
can look only in one direction at a time. The functionality reproduced
by the \ccg~model is `the selection of the best target end-point for a
reflexive saccade'. A competition such as this between incompatible
movements is often referred to as an \e{action selection}
problem \citep{norman_attention_1986,maes_dynamics_1989,redgrave_basal_1999}.}

\rvwt{One hypothesis for the r\^ole played by the basal ganglia (BG)
is that the system performs \e{action selection}
\citep{mink_basal_1996,redgrave_basal_1999,hikosaka_role_2000}.
The \ccg~model places the BG at the centre of the oculomotor system,
following the known anatomy of the
region \citep{hikosaka_role_2000}. The BG receives input indirectly
from the superior colliculus, which has a retinotopic
arrangement \citep{ottes_visuomotor_1986}.
%and a signal which is associated with saccadic eye
%movements \citep{wurtz_superior_1971}, specifying the saccade
%end-point.
The BG receives excitatory
inputs directly from retinotopic regions of the cortex including the
frontal eye fields (FEF), supplementary eye fields (SEF), lateral
intraparietal cortex (LIP) and dorsolateral prefrontal cortex. The
dorsolateral prefrontal cortex, which participates in voluntary
saccades
\citep{funahashi_prefrontal_1993,munoz_look_2004}, is not
modelled because the model concerns reflexive rather than voluntary
eye movements. Several other regions of the brain that are associated
with eye movements are also omitted from the model. The early visual
processing stream in cortex, from V1, through to the LIP is subsumed
into a `sustained retinal' signal. The justification here is that the
model reacts to simple luminant targets and does not need to carry out
the feature extraction performed by these visual areas. The
supplementary eye fields are involved in the programming of saccade
sequences \citep{tehovnik_eye_2000} and memory guided
saccades \citep{chen_supplementary_1995,schlag_neurons_2002}. Lesions
of SEF do not affect visually guided
saccades \citep{gaymard_cortical_1998} and so the SEF is also omitted
from the model.}
%
% Figure here is the ``macroscopic architecture'' one.
%

% Now describe each bit a little more, with help of the figure.
\rvwt{Fig.~\ref{fig:ccg_model}(a) shows the macroscopic architecture of
the \ccg~model. The figure shows the relationships between the retinal
input populations, the FEF, the populations comprising the BG
sub-system (the red border indicates that the box represents a number
of populations as a sub-system), the thalamus and the superior
colliculus. Excitatory connections are indicated with arrow heads;
inhibitory connections with circles in place of the arrow heads. The
blue and green connection lines indicate two thalamo-basal ganglia
loops, one cortical loop through FEF (green), the other a sub-cortical
loop through SC. It is important to note that although they are given
different colours in the diagram, these loops are in no way
independent, with loop activity combining both in thalamus and in the
basal ganglia and a direct excitatory, feed-forward connection from
FEF to SC.}

% More on BG model here
\rvwt{The basal ganglia sub-system is the most complex component of
the \ccg~model. The BG model is based on previous
work \citep{gurney_computational_2001,gurney_computational_2001-1} and is referred to as the GPR
model. The GPR model incorporates the following main components of the
primate BG \citep{mink_basal_1996,wickens_basal_1997}: (i) The
striatum (the main input station to the BG) which is divided into two
iterdigitated poulations of projection neurons expressing primarily D1
or D2-type dopaminergic receptors (named Str\_D1 and Str\_D2); (ii)
The subthalamic nucleus (STN); (iii) the external segment of the
globus pallidus (GPe); (iv) the output nucleus relevant for saccadic
control---the substantia nigra pars reticulata
(SNr) \citep{hikosaka_role_2000}.}

\rvwt{The connectivity of the GPR model (Fig.~\ref{fig:ccg_model}(b)
is constrained by the known anatomy and physiology of the
BG~\citep{bolam_synaptic_2000}. Physiologically, the only source of
glutamate within the BG is the STN, whose projections are therefore
excitatory; all other nuclei have GABAergic projection neurons and are
therefore inhibitory. The cortex sends glutamatergic projections to
both the Str\_D1 striatal population, which projects preferentially to
the SNr, and to Str\_D2, which projects primarily to
GPe \citep{gerfen_d1_1990}. The cortex also projects to the STN, which
sends diffuse projections to the SNr and
GPe \citep{parent_anatomical_1993}. The GPe projects to the SNr and
also projects back to the STN, completing a GPe--STN loop.}

\rvwt{Within the BG, there are several mechanisms supporting
competitive processing for selecting channels whose inhibitory output
is reduced. The selection mechanism of the GPR model is the
`off-centre, on-surround' scheme proposed
by \cite{mink_basal_1993}. The `on-surround' is provided by
diffuse, excitatory projections from the STN to the SNr. Focussed
inhibition from the Str\_D1 neurons in striatum contributes the
`off-centre' part of the mechanism. This arrangement leads to
selection behaviour via a release of target inhibition, since
channels that have strong saliencel (input) have weak output at the
level of SNr, and channels with weak salience have enhanced output.}

\rvwt{The GPe is not included in the centre-surround circuit described
above, but still plays a key r\^ole in selection. Operating alone, the
Str\_D1/STN/SNr circuit can suffer from the following problem: if the
input for all channels is relatively high, then the diffuse projection
from STN, which effectively supplies a sum of the STN inputs to each
channel in SNr, will provide so much excitation that Str\_D1 may
become unable to inhibit one of the channels in SNr and selection may
become
impossible. \cite{gurney_computational_2001,gurney_computational_2001-1}
showed that the inhibitory feedback from GPe to STN acts as an
`automatic gain control' to help prevent this from occurring.}

\rvwt{At the neuronal level, the STN, GPe and SNr have tonic output
levels \citep{chevalier_disinhibition_1990,delong_primate_1985,kita_intracellular_1991}. This
is modelled using piecewise linear output functions with zero offsets,
$c$ (see Eq.~\ref{eq:lintransfunc}). In striatum, Str\_D1 and Str\_D2
have positive offset $c$, mimicking the so-called `down-state' of
medium spiny neurons which have a resting potential far below spiking
threshold and require co-ordinated input to generate action
potentials \citep{wilson_origins_1996}.
% Note, in Cope's paper, there is an error with the offsets for
% D1,D2. These are set to -0.05 instead of 0.05. A quick trial with
% the model suggests this doesn't make a very large difference to the
% operation, and I have the sign correct in any case.
In addition, the Str\_D1 and Str\_D2 neurons are influenced by
dopamine in different ways; facilitating cortico-striatal transmission
at medium spiny neurons with D1 receptors \citep{hernandez-lopez_D1_1997,gonon_prolonged_1997} and reducing
transmission at those with D2 receptors \citep{delgado_inhibitory_1999}. These effects are
modelled using a dopamine parameter which modulates the input
activation as described below in Eqs~\ref{eq:a_in_d1} \& \ref{eq:a_in_d2}.}

% Change this - we already talked about channels?
\rvwt{The \ccg~model adopts a `channel based' model from previous
work~\citep{redgrave_basal_1999,gurney_computational_2001}.
Within the context of the basal ganglia model, a `channel' is a
sub-set of neurons which are associated with an individual
action. Each channel in BG loops back via relays in the thalamus
through cortex. Input into this thalamo-cortical loop is termed
`salience'. Because it is a loop, input salience to the channel may
originate cortically or sub-cortically. The higher the salience of the
channel, the greater is the behavioural relevance of the associated
action.}

\rvwt{In the oculomotor model, an action
corresponds to a distinct saccade end point. It can be seen that the
action space for reflexive saccade end points is therefore
continuous rather than discrete. MORE HERE}

% FEF stuff taken from Alex's pre-pub

Fig.~\ref{brain_model} shows the layout of the populations in the
brain model, as implemented in SpineCreator, and the interconnections
between them. Each population of 2500 elements is arranged as a 50 by
50 grid which forms a map in a retinotopic co-ordinate system, roughly
matching the known layout of the superior
colliculus \citep{robinson_eye_1972}.
% and frontal eye field?

@@

The output, $y$, of LINlinear is related to the activation $a$ by the
piecewise linear transfer function
\begin{equation} \label{eq:lintransfunc}
   y(a) = \begin{cases}
      0   & a < c \\
      a-c & c \leq a \leq 1+c \\
      1   & a > 1+c
   \end{cases}
\end{equation}
where $c$ is a parameter defining the offset of the transfer
function. \rvwt{If $c<0$, then for zero activation ($a=0$), the output
will be positive. This simulates the effect of a neural population
having tonic firing. If $c>0$ then the output will be zero until the
activation exceeds $c$, simulating neurons which only fire when driven
by excitatory input.} At this point, the naming scheme for the
component becomes apparent; this is a Leaky Integrator with a
piecewise-linear transfer function.

@@

The D1MSN and D2MSN components are both leaky integrators, similar to
LINlinear. They differ in that they have no shunting inhibition. They
are used to model medium spiny neuron (MSN) populations in the
striatum. As they model the fact that most MSN neurons fall into two
groups; those expressing D1 dopamine receptors and those expressing D2
receptors, they have a dopamine parameter that modulates the input
activation, so that their equations for $a_{in}$ are thus:
\begin{equation} \label{eq:a_in_d1}
   a_{in}^{D1} = (0.2 + d)A + 0.01 R_N
\end{equation}
\begin{equation} \label{eq:a_in_d2}
   a_{in}^{D2} = (1 - d)A + 0.01 R_N
\end{equation}
where $d$ is the dopamine parameter. Varying dopamine from 0 to 1
enhances the activation in the D1 model, whereas it decreases the
activation of the D2 model elements, in line with experimental
observations \citep{harsing_influence_1997,gonon_prolonged_1997}.
Note that the equation for $a_{in}^{D1}$ differs from that used in
the \ccg~model, for which the cortico-striatal weights are multiplied
by $(1+d)$ rather than $(0.2+d)$.

@@

\cite{tabareau_geometry_2007} give a formulation for the weight maps
in which it is possible to project both a positive and a negative
weight. In our model, all projections from SC\_deep are excitatory.
This means that each channel has a weight which follows the form:
\begin{equation} \label{eq:weightmaps}
w(r,\phi) = i\;e\,^{jr}\;\sin\left(\frac{2\pi\phi}{W_{nfs}} + k\right)
\end{equation}
where $i$, $j$ and $k$ are per-channel parameters for the weight
maps. $k$ is determined by the mapping. Only the positive part of the
sine is utilised. $i$ and $j$ are parameters to be found.

@@

% worldDataMaker to brain:
The eye model outputs its rotational state at each timestep. The
rotational state is used to compute the view of the world in the eye's
frame of reference. To simplify the calculation, the luminances exist
on a spherical surface at the centre of which is the eye. A hand-coded
BRAHMS component called worldDataMaker computes the projection of the
luminances into the eye's frame of reference and then converts this
representation into a retinotopic map to pass into the brain
model. The input to the brain model is thus able to change
continuously, on every timestep, rather than in a step-wise fashion
when a saccade occurs, as in the \ccg~model.

@@

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/ccg_model.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:ccg_model} Figure \arabic{figure}.}
{ The macroscopic architecture of the \ccg~model. The main nuclei
modelled as brain systems are: basal ganglia (BG), frontal eye fields
(FEF), thalamus (THAL) and superior colliculus (SC). The retinal input
is presented via non-biologically plausible retinal populations. The
loops through basal ganglia, which define the architecture, are shown
with coloured lines: the cortical loop (through FEF and THAL) in green
and the sub-cortical loop (through SC and THAL) in blue. Connections
with arrowheads indicate excitatory connections, those with circles
are inhibitory. A red border indicates that the box represents a
sub-system of two or more populations; a black box indicates,
within the context of the model, a single neural population.}
\end{figure}
